LDATS Rodents Example

### 2019-02-14 doc/rodents-example.Rmd
adding the library call to the example vignette

To obtain the most recent version of **LDATS**, install the most recent 
version from GitHub:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("weecology/LDATS")
```

>>>>

To obtain the most recent version of **LDATS**, install and load the most recent 
version from GitHub:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("weecology/LDATS")
library(LDATS)
```
